A Survey on Ordered Binary Decision Diagrams

### 2015-09-14 paper.tex
Add paragraph describing the minimized OBDD example

The sifting algorithm therefore uses a brute-force enumeration strategy to find
the optimal variable position. It starts by swapping the processed variable $x$
downwards one level at a time, i.e. swapping it with its successor variable, which
is located on the layer below in the OBDD. This is done until $x$ is the next to
last variable in the OBDD. Then, this is done in the other way round, i.e. swapping
$x$ with its predecessor variable until $x$ becomes the top variable of the OBDD.
While proceeding, the ideal position is memorized and after $x$ became the top
variable, $x$ is moved to this ideal position by, again, swapping levels one by
one~\cite{RUDELL93}. Figure~\ref{fig:sifting-algorithm} shows this procedure
applied to an example, requiring a total of 9 steps for 5 possible positions.

@@

>>>>

The sifting algorithm therefore uses a brute-force enumeration strategy to find
the optimal variable position. It starts by swapping the processed variable $x$
downwards one level at a time, i.e. swapping it with its successor variable, which
is located on the layer below in the OBDD. This is done until $x$ is the next to
last variable in the OBDD. Then, this is done in the other way round, i.e. swapping
$x$ with its predecessor variable until $x$ becomes the top variable of the OBDD.
While proceeding, the ideal position is memorized and after $x$ became the top
variable, $x$ is moved to this ideal position by, again, swapping levels one by
one~\cite{RUDELL93}. Figure~\ref{fig:sifting-algorithm} shows this procedure
applied to an example, requiring a total of 9 steps for 5 possible positions. The
first phase, determining the ideal position by swapping two variables at a time,
is marked red, i.e. the two swapped variables are marked. The variable pairs
swapped during the second phase, i.e. moving the $x$ to its ideal position (4),
are marked green.

@@

However, dynamic variable ordering is a good practice to obtain minimized OBDDs.
For example, Figure~\ref{fig:min-obdd} shows the minimized, and thus optimal, OBDD
representation of \newline $f=\left(A \land B\right) \lor \left(B \land C\right)$
which, compared to the OBDD shown in Figure~\ref{subfig:obdd}, consists of less
nodes.
